Modal Verification Patterns for Systems

### 2025-06-23 paper.tex
+

\todo[inline]{Colin says: I don't think this section needs to change much,
but it should be read carefully with the new audience in mind,
possibly giving more details on what systems concepts each system is dealing with, for a non-systems audience.}
\paragraph{Shallow Modalities in Iris Separation Logic}
\label{sec:modal_in_iris}
\todo[inline,color=cyan]{this also seems taken from the VMM work}
Classically modal operators are given direct semantics in terms of an underlying model, which for \textsf{Iris} would be a collection of \textsc{CMRA}s; this is the case for \textsf{Iris}'s one built-in modality for step-indexing~\cite{krebbers2017essence}. However in general, many modalities can be given proof-theoretic semantics directly within a logic. This is the case for \textsf{Iris}'s weakest precondition modality (which is defined within the \textsf{Iris} logic itself), as well as for a wide range of other modalities in the literature~\cite{restall2002introduction}. These modalities are typically multi-modal, with a form of roughly $M~\overline{ctxt}~\phi\triangleq\ldots\rightarrow \phi~\overline{ctxt}$. In a substructural setting~\cite{restall1993modalities,krebbers2017essence} the implication $\rightarrow$ is typically replaced with substructural implication $\sepimp$.

>>>>

\todo[inline]{Colin says: I don't think this section needs to change much,
but it should be read carefully with the new audience in mind,
possibly giving more details on what systems concepts each system is dealing with, for a non-systems audience.}
\paragraph{Shallow Modalities in Iris Separation Logic}
\label{sec:modal_in_iris}
\todo[inline,color=cyan]{this also seems taken from the VMM work}
\todo[inline,color=pink]{this text has never been part of any text that is either submitted or made publicly available.}
Classically modal operators are given direct semantics in terms of an underlying model, which for \textsf{Iris} would be a collection of \textsc{CMRA}s; this is the case for \textsf{Iris}'s one built-in modality for step-indexing~\cite{krebbers2017essence}. However in general, many modalities can be given proof-theoretic semantics directly within a logic. This is the case for \textsf{Iris}'s weakest precondition modality (which is defined within the \textsf{Iris} logic itself), as well as for a wide range of other modalities in the literature~\cite{restall2002introduction}. These modalities are typically multi-modal, with a form of roughly $M~\overline{ctxt}~\phi\triangleq\ldots\rightarrow \phi~\overline{ctxt}$. In a substructural setting~\cite{restall1993modalities,krebbers2017essence} the implication $\rightarrow$ is typically replaced with substructural implication $\sepimp$.
